An Improved ANS Transaction Template

### 2018-01-26 paper.tex
adding table case 2

\subsubsection{Case 2}
The case 2 is design is also limited to 30 cascades in the scenario (limit of
the JCPOA agreement), all design the same way. In thsi case the explored design
aims to reproduce the different stage of the reference case over the different
level of cascade enrichment: the goal is to have the tails assay of a stage to
match the feed assay of the previous stage. To do so instead of aiming for a
S/E stages of 4/10, a S/E stages repartition of 6/7 was targeted.:w

The design properties are:\\
- less than 169 centrifuges per cascade,\\
- F/P/T assays: 0.0071/0.0296/0.002.\\% to be correct with the correct value --
                                      % this corresponds to a S/E of 5/6
The corresponding design is:\\
- 167 centrifuges,\\
- F/P/T assays: 0.0071/0.0260104/0.0019111.\\

Both case 1 and 2 will be simulation without and with tail recycling. In the
tail recycling cases, the tails of the cascade level $N$ are blended in the feed
of cascade level $N-1$.

@@

Later on, we can include a table, even one that spans two columns such as
Table~\ref{tab:widetable}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[htb]
  \centering
\begin{tabular}{llllllllll}\toprule
      & $\phi_T(0)$      & $\phi_T(10)$      & $\phi_T(20)$      &
      $\phi_D(0)$      & $\phi_D(10)$      & $\phi_D(20)$      & $\rho$      &
      $\varepsilon$      & $N_\text{it}$
\\ \midrule
$c=0.999$  & 0.9038 & 20.63 & 31.24 & 0.9087 & 20.63 & 31.23 & 0.2192 & $10^{-7}$ & 15
\\
$c=0.990$  & 0.3675 & 13.04 & 24.7 & 0.3696 & 13.04 & 24.69 & 0.2184 & $10^{-7}$ & 15
\\
$c=0.900$  & 0.009909 & 4.776 & 17.64 & 0.009984 & 4.786 & 17.63 & 0.2118 & $10^{-7}$ & 14
\\
$c=0.500$  & $6.069\times 10^{-5}$ & 2.212 & 15.53 & 6.213$\times 10^{-5}$ & 2.239 & 15.53 & 0.2068 & $10^{-7}$ & 13
\\
\bottomrule
\end{tabular}
  \caption{This is an example of a really wide table which might not normally
  fit in the document.}
  \label{tab:widetable}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Notice how the table reference uses a Roman numeral
for its numbering scheme, whereas the figure reference uses an Arabic numeral.
For one-column tables, use the \verb|table| environment; two-column tables use
\verb|table*|. The same applies to figures.

>>>>

\subsubsection{Case 2}
The case 2 is design is also limited to 30 cascades in the scenario (limit of
the JCPOA agreement), but this time each level of cascade are designed to get
feed with the previous level product and to have 4 stripping stages and 10
enriching stages. The configuration of the different level of cascade can be
found in table \ref{}
\begin{table}[htb]
\centering
\begin{tabular}{lllll}
\toprule

Level   &           & Assay     &       & Machines  \\ 
        & Feed      & Product   & Feed  &           \\
\midrule
1       & 0.0071    & 0.0413    & 0.0029 & 167       \\
2       & 0.0413    & 0.2043    & 0.0173 & 169       \\
3       & 0.2043    & 0.5941    & 0.0971 & 168       \\
4       & 0.5941    & 0.8834    & 0.3915 & 168       \\
5       & 0.8834    & 0.9735    & 0.7746 & 169       \\

\bottomrule
\end{tabular}
  \caption{Summary of the different properties of the different level of cascade.}
  \label{tab:widetable}
\end{table}

@@

Later on, we can include a table, even one that spans two columns such as
Table~\ref{tab:widetable}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Notice how the table reference uses a Roman numeral
for its numbering scheme, whereas the figure reference uses an Arabic numeral.
For one-column tables, use the \verb|table| environment; two-column tables use
\verb|table*|. The same applies to figures.
